---
header-includes:
- \usepackage{hyperref}
- \usepackage{graphicx}
- \graphicspath{{stat-tables_files/figure-latex/}}
- \usepackage{geometry}
- \geometry{a4paper,left=.6in,right=.6in,top=1in,bottom=1in}
output:
  pdf_document:
    keep_tex: yes
---

```{r setup, include = FALSE}
library(knitr)
library(tidyverse)
library(kableExtra)
library(iprior)
library(crayon)
library(purrr)
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, fig.path = "figure/", 
                      cache.path = "_cache/", fig.width = 9, fig.height = 5)
```

\thispagestyle{empty}
\begin{center}
~\\
\vspace{2cm}
{\Huge Statistical Tables}
~\\~\\
v1.00 (last updated: 27 Nov 2024)
\vspace{5cm}
\end{center}

```{r, fig.height = 3, fig.width = 6,out.width = "\\textwidth", warning = FALSE, fig.align = "center"}
x <- seq(-3, 3, length = 3000)
y <- dnorm(x)
dat <- tibble(x, y)
ggplot(dat, aes(x, y)) +
  # geom_line() +
  geom_ribbon(aes(ymax = y, ymin = 0), alpha = 0.5, col = NA) +
  geom_col(aes(fill = x)) +
  scale_fill_gradientn(colours = iprior::gg_col_hue(10)[c(4:10, 1:3)]) +
  theme_void() +
  theme(legend.position = "none")
```

\vfill
\begin{center}
Copyright (c) 2024--present SKY-TKP
~\\
\href{https://github.com/SKY-TKP}{\texttt{https://github.com/SKY-TKP}}
\end{center}

\newpage
### Summary some distribution 
Discrete Probability Distribution

| **Distribution**  | **Parameter** |                 **Probability mass function; PMF**                 |     **Expected Value**    |                        **Variance**                        |
|-----------------------------|:-------------:|:------------------------------------------------------------------:|:---------------:|:---------------------------------------:|
| Uniform           |     $a, b$    | $\frac{1}{b - a + 1}$                    | $\frac{a+b}{2}$ |                  $\frac{(b-a+1)^2-1}{12}$                  |
| Binomial          |     $n, p$    | $\binom{n}{k}p^k\ (1-p)^k$                               |       $np$      |                            $npq$                           |
| Poisson           |   $\lambda$   | $\frac{e^{-\lambda}{\lambda}^x}{x!}$                     |    $\lambda$    |                          $\lambda$                         |
| Geometric         |      $p$      | $(1-p)^{k-1}p$                                          |  $\frac{1}{p}$  |                      $\frac{1-p}{p^2}$                     |
| Hypergeometric    |   $M, N, n$   | $\frac{{M \choose k} {N-M \choose n-k}}{{N \choose n}}$ | $n \frac{M}{N}$ | $n \frac{M}{N} \left(1-\frac{M}{N}\right) \frac{N-n}{N-1}$ |
| Negative Binomial |     $r, p$    | ${k-1 \choose r-1} p^r (1-p)^{k-r}$                     | $\frac{r}{p}$   |                    $\frac{r(1-p)}{p^2}$                    |

Continuous Probability Distribution

| **Distribution** | **Probability density function; PDF**                                                                                                                         | **Expected Value**       | **Variance**                                            | **Note****     |
|------------------------------------------------------|:-------------------------------------------------------------------------------------------------------------------------------------------------------------:|:------------------------:|:-------------------------------------------------------:|:------------:|
| Uniform          | $\frac{1}{b - a}$                                                                                                                                             | $\frac{a+b}{2}$          | $\frac{(b-a)^2}{12}$                                    | -            |
| Normal           | $\frac{1}{\sigma\sqrt{2\pi}}e^{ -\frac{1}{2}\left(\frac{x-\mu}{\sigma}\right)^{\!2}}$                                                          | $\mu$                    | $\sigma$                                                | -            |
| Z (S.M)*              | $\frac{1}{\sqrt{2\pi}}e^{-\frac{1}{2}z^{\!2}}$                                                                                                | 0                        | 1                                                       | -            |
| Exponential      | ${\lambda}{e^{-{\lambda}x}}$                                                                                                                         | $\frac{1}{\lambda}$      | $\frac{1}{\lambda^2}$                                   | -            |
| Erlang          | $\frac{\lambda^k x^{k-1} e^{-\lambda x}}{(k-1)!}$                                                                            | $\frac{k}{\lambda}$      | $\frac{k}{\lambda^2}$                                   |              |
| Chi-squared         | $\frac{1}{2^{n/2}\Gamma(n/2)}x^{(n/2)-1}e^{-x/2}$                                                                                                             | $n$                      | $2n$                                                    | $df$         |
| Student's $t$              | $\frac{\Gamma((n+1)/2)}{\sqrt{\pi n}\,\Gamma(n/2)}\left(1+\frac{t^2}{n}\right)^{-\frac{n+1}{2}}$                                                              | 0                        | $\frac{n}{n-2}$                                         | $df$         |
| F-distribution              | $\frac{\Gamma((n_1+n_2)/2)}{\Gamma(n_1/2)\Gamma(n_2/2)}\left(\frac{n_1}{n_2}\right)^{n_1/2}x^{(n_1/2)-1}\left(1+\frac{n_1}{n_2}x\right)^{-\frac{n_1+n_2}{2}}$ | $\frac{n_2}{n_2 - 2}$    | $\frac{2n_2^2(n_1 + n_2 - 2)}{n_1(n_2 - 2)^2(n_2 - 4)}$ | $df_1, df_2$ |
| Gamma          | $\frac{\lambda^{\alpha} x^{\alpha - 1} e^{-\lambda x}}{\Gamma(\alpha)}$                                                                                       | $\frac{\alpha}{\lambda}$ | $\frac{\alpha}{\lambda^2}$                              | -            |

*$S.M: Standard \ Normal \ Distribution$

**$df = n - 1$

\newpage
### Summary some distribution - cont.

| **Distribution** | **Notation** | **Domain** | **Moment Generating Function; MGF** |
|-----|---|-----|:---:|
| **Discrete Distributions** |  |  |
| Uniform discrete | $Uniform(a, b)$| $\{a, a+1, ..., b\}$ |$\frac{e^{at}-e^{bt}}{t(b-a)}$ |
| Binomial | $Bin(n, p)$ | $\{0, 1, 2, ..., n\}$ | $(pe^t + q)^n$, $q = 1-p$ |
| Poisson | $Poi(\lambda)$ | $\{0, 1, 2, ...\}$ | $e^{\lambda(e^t-1)}$ |
| Geometric | $Geo(p)$ | $\{1, 2, 3, ...\}$ | $\frac{pe^t}{1-qe^t}$, $q = 1-p$ |
| Hypergeometric | $Hyper(M,N,n)$ | $\{0, 1, 2, ..., min(M, n)\}$ | - |
| Negative binomial | $NB(r, p)$ | $\{0, 1, 2, ...\}$ |$(\frac{pe^t}{1-qe^t})^r$, $q = 1-p$ |
| **Continuous Distributions** |  |  |
| Uniform continuous | $Uniform(a, b)$ | $[a, b]$ | $\frac{e^{bt}-e^{at}}{t(b-a)}$ |
| Normal | $Normal(\mu, \sigma^2)$ | $(-\infty, \infty)$ | $e^{{\mu}t + \frac{1}{2}\sigma^2t^2}$ |
| Z (Standard Normal) |  $Z(0, 1)$ |$(-\infty, \infty)$ | $e^{\frac{1}{2}t^2}$ |
| Exponential | $Expo(\lambda)$ |$[0, \infty)$ | $\frac{\lambda}{\lambda-t}$, t < $\lambda$ |
| Erlang | $Er(k,\ \lambda)$ |$[0, \infty)$ and $k = 0, 1, 2, ..$ | $(\frac{\lambda}{\lambda-t})^k$, t < $\lambda$ |
| Chi-squared | $\chi^2(n)$ | $[0, \infty)$ | $(1-2t)^{-\frac{n-1}{2}}$, t < $\frac{1}{2}$ |
| Student's $t$ | $T(n)$ |$(-\infty, \infty)$ | - |
| F-distribution | $F(n_1, n_2)$|$[0, \infty)$ | - | |
| Gamma | $Gamma(\alpha,\ \lambda)$| $[0, \infty)$ | $(1-\beta t)^{-\alpha}$, t <$\frac{1}{\beta}$ 


\newpage
### Table 1: Cumulative probabilities of the standard normal distribution.

Each table entry is the area $\alpha$ under the standard normal curve from $-\infty$ to $z(\alpha)$.
That is, the entries are $\int_{-\infty}^{z(\alpha)}f_Z(z) \, dz = \alpha$, where $f_Z$ is the pdf of $Z\sim \text{N}(0,1)$.

\vspace{1em}

```{r, fig.height = 3, fig.width = 6,out.width = "6cm", warning = FALSE, fig.align = "center"}
x <- seq(-3, 3, length = 200)
y <- dnorm(x)
dat <- tibble(x, y)
ggplot(dat, aes(x, y)) +
  geom_line() +
  geom_ribbon(data = subset(dat , x >= -3 & x <= -0.4), aes(ymax = y),
              ymin = 0, fill = iprior::gg_col_hue(1), colour = NA,
              alpha = 0.5) +
  geom_line(data = tibble(xx = c(-0.4, -0.4), yy = c(0, dnorm(0.4))),
            aes(xx, yy), linetype = "dashed") +
  # annotate("text", x = -0.25, y = 0.17, size = 5, 
  #          label = expression("A ="~P (Z<z[alpha]) )  ) +
  annotate("text", x = -0.85, y = 0.17, size = 8, label = expression(alpha)) +
  labs(x = NULL, y = NULL) +
  scale_x_continuous(breaks = -0.4, labels = expression(z(alpha))) +
  theme_classic() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 20))
```

```{r normtab}
u <- seq(-3.49, 0 , by = 0.01)
p <- pnorm(u)
m <- matrix(p, ncol = 10, byrow = TRUE)  

m <- m[, c(10, 9, 8, 7, 6, 5, 4, 3, 2, 1)]  

m <- formatC(m, format = "f", digits = 4)  # จัดรูปแบบตัวเลข
m <- data.frame(m)
colnames(m) <- c(
  gsub("0.0", ".0", iprior::dec_plac(seq(0, 0.09, by = 0.01), 2))
)
rownames(m) <- c(
  iprior::dec_plac(seq(-3.4, 0, by = 0.1), 1)
)
m <- cbind("z" = rownames(m), m)

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE) %>%
  kable_styling(position = "center")
```

\newpage
### Table 2: Percentiles of the $\chi^2$-distribution.

Each table entry is $\chi^2_k(\alpha)$, where $\int_{\chi^2_k(\alpha)}^{\infty}f_X(x) \, dx = \alpha$ with $X\sim\chi^2_k$.

```{r, fig.height = 2.7, fig.width = 6, out.width = "6cm", warning = FALSE, fig.align = "center"}
x <- seq(0, 10, length = 250)
y <- dchisq(x, df = 3.3)
dat <- tibble(x, y)

ggplot(dat, aes(x, y)) +
  geom_line() +
  geom_ribbon(data = subset(dat , x > 6), aes(ymax = y),
              ymin = 0, fill = iprior::gg_col_hue(1), colour = NA,
              alpha = 0.5) +
  geom_line(data = tibble(xx = c(6, 6), yy = c(0, dchisq(6, 3.3))),
            aes(xx, yy), linetype = "dashed") +
  geom_curve(x = 7, y = 0.02, xend = 8, yend = 0.08, 
           curvature = -0.15, 
           arrow = arrow(length = unit(0.2, "cm"), type = "closed")) +  
  annotate("text", x = 8.40, y = 0.09, size = 9, label = expression(italic(alpha))) +
  labs(x = NULL, y = NULL) +
  scale_x_continuous(breaks = c(0, 6), 
                     labels = c(0, expression(chi[k]^2 ~(alpha)))) +
  theme_classic() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 20))
```

```{r chisqtab}
alpha_ <- expression(alpha)
u <- c(0.005, 0.010, 0.025, 0.050, 0.100, 0.500, 0.900, 0.950, 0.975, 0.990, 0.995)
k <- c(seq(1, 29, by = 1), seq(30, 100, by = 10))
m <- data.frame(matrix(NA, ncol = length(u), nrow = length(k)))


for (i in seq_along(k)) {
  m[i, ] <- qchisq(1 - u, df = k[i])
}

colnames(m) <- iprior::dec_plac(u, 3)
# rownames(m) <- k
m <- cbind("k" = k, iprior::dec_plac(m, 3))

options(digits = 4)
kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE, 
      align = c("l", rep("r", length(u)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$Area$" = 11), escape = FALSE)
```

\newpage
### Table 3: Percentiles of Student's $t$-distribution.

Each table entry is $t_k(\alpha)$, where $\int_{t_k(\alpha)}^{\infty}f_X(x) \, dx = \alpha$ with $X\sim T_k$.


```{r, fig.height = 3, fig.width = 6,out.width = "6cm", warning = FALSE, fig.align = "center"}
x <- seq(-3, 3, length = 200)
y <- dt(x, df = 1)
dat <- tibble(x, y)
ggplot(dat, aes(x, y)) +
  geom_line() +
  geom_ribbon(data = subset(dat , x <= 3 & x >= 0.8), aes(ymax = y),
              ymin = 0, fill = iprior::gg_col_hue(1), colour = NA,
              alpha = 0.5) +
  geom_line(data = tibble(xx = c(0.8, 0.8), yy = c(0, dt(0.8, 1))),
            aes(xx, yy), linetype = "dashed") +
  annotate("text", x = 1.30, y = 0.06, size = 10, label = alpha_) +
  labs(x = NULL, y = NULL) +
  scale_x_continuous(breaks = 0.8, labels = expression(t[k]~(alpha) )) +
  theme_classic() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 20))
```

```{r ttab}
u <- 1 - c(0.60, 0.70, 0.80, 0.85, 0.90, 0.95, 0.975, 0.99, 0.9925, 0.995, 0.9975, 0.9995)
k <- c(seq(1, 40, by = 1), c(50, 60, 100, 120, Inf))
m <- data.frame(matrix(NA, ncol = length(u), nrow = length(k)))
for (i in seq_along(k)) {
  m[i, ] <- -1*(qt(u, df = k[i]))
}
colnames(m) <- c(
  iprior::dec_plac(1- c(0.60, 0.70, 0.80, 0.85, 0.90, 0.95), 2),
  iprior::dec_plac(1 - c(0.975, 0.99), 3),
  iprior::dec_plac(1 - c(0.9925, 0.995, 0.9975, 0.9995), 4)
)
m <- cbind("k" = k, iprior::dec_plac(m, 3))
m[nrow(m), 1] <- "Infinity"

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE, 
      align = c("l", rep("r", length(u)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$Area$" = length(u)), escape = FALSE)
```

\newpage
### Table 4.1: Percentiles of the $F$-distribution.

Each table entry is $F_{k_1,k_2}(\alpha) = F_{k_2,k_1}^{-1}(1-\alpha)$, where $\int_{F_{k_1,k_2}(\alpha)}^{{\infty}}f_X(x) \, dx = \alpha$ with $X\sim F_{k_1,k_2}$.

```{r, fig.height = 2.6, fig.width = 6,out.width = "6cm", warning = FALSE, fig.align = "center"}
x <- seq(0, 10, length = 250)
y <- df(x, df1 = 10, df2 = 3)
dat <- tibble(x, y)
ggplot(dat, aes(x, y)) +
  geom_line() +
  geom_ribbon(data = subset(dat , x > 4), aes(ymax = y),
              ymin = 0, fill = iprior::gg_col_hue(1), colour = NA,
              alpha = 0.5) +
  geom_line(data = tibble(xx = c(4, 4), yy = c(0, df(6, 10, 2))),
            aes(xx, yy), linetype = "dashed") +
  geom_curve(x = 5, y = 0.02, xend = 6.5, yend = 0.15, 
           curvature = -0.15, 
           arrow = arrow(length = unit(0.1, "cm"), type = "closed")) +  
  annotate("text", x = 7, y = 0.15, size = 9, label = expression(alpha)) +
  labs(x = NULL, y = NULL) +
  scale_x_continuous(breaks = c(0, 4), 
                     labels = c(0, expression(F[k[1]~","~k[2]] ~(alpha)))) +
  theme_classic() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 20))
```


```{r ftab1}
u <- c(0.500, 0.100, 0.050, 0.025, 0.010, 0.005, 0.001)
u_format <- format(u, nsmall = 3)
k1 <- 1:10
k2 <- 1:5
uk2 <- expand.grid(u, k2)
m <- data.frame(matrix(NA, ncol = length(k1), nrow = nrow(uk2)))
for (i in seq_len(nrow(uk2))) {
  for (j in seq_along(k1)) {
    m[i, j] <- qf(1 - uk2[i, 1], df1 = k1[j], df2 = uk2[i, 2])
  }
}
tmp <- m

# k2 = 1
m[1, ] <- iprior::dec_plac(tmp[1, ], 3)
m[2, ] <- iprior::dec_plac(tmp[2, ], 2)
m[3:7, ] <- round(tmp[3:7, ], 1)

# k2 = 2
m[8:9, ]   <- iprior::dec_plac(tmp[8:9, ], 3)
m[10:14, ] <- iprior::dec_plac(tmp[10:14, ], 2)

# k2 = 3
m[15:17, ] <- iprior::dec_plac(tmp[15:17, ], 3)
m[18:19, ] <- iprior::dec_plac(tmp[18:19, ], 2)
m[20:21, ] <- iprior::dec_plac(tmp[20:21, ], 1)

# k2 = 4
m[22, ] <- iprior::dec_plac(tmp[22, ], 3)
m[23:25, ] <- iprior::dec_plac(tmp[23:25, ], 2)
m[26:28, ] <- iprior::dec_plac(tmp[26:28, ], 1)

# k2 = 5
m[29, ] <- iprior::dec_plac(tmp[29, ], 3)
m[30:32, ] <- iprior::dec_plac(tmp[30:32, ], 2)
m[33:35, ] <- iprior::dec_plac(tmp[33:35, ], 1)

colnames(m) <- k1
m <- cbind("Area" = rep(as.character(u_format), length(k2)), m)

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE,
      align = c("l", rep("r", length(k1)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$k_1$" = length(k1)), escape = FALSE) %>%
  # collapse_rows(1, latex_hline = "none", row_group_label_position = "stack")
  pack_rows("$k_2=1$", 1, 7, escape = FALSE) %>%
  pack_rows("$k_2=2$", 8, 14, escape = FALSE) %>%
  pack_rows("$k_2=3$", 15, 21, escape = FALSE) %>%
  pack_rows("$k_2=4$", 22, 28, escape = FALSE) %>%
  pack_rows("$k_2=5$", 29, 35, escape = FALSE)
```

\newpage
### Table 4.2: (Continued) Percentiles of the $F$-distribution.

```{r ftab2}
u <- c(0.500, 0.100, 0.050, 0.025, 0.010, 0.005, 0.001)
u_format <- format(u, nsmall = 3)
k1 <- c(11, 12, 13, 14, 15, 20, 30, 60, 120, Inf)
k2 <- 1:5
uk2 <- expand.grid(u, k2)
m <- data.frame(matrix(NA, ncol = length(k1), nrow = nrow(uk2)))
for (i in seq_len(nrow(uk2))) {
  for (j in seq_along(k1)) {
    m[i, j] <- qf(1 - uk2[i, 1], df1 = k1[j], df2 = uk2[i, 2])
  }
}
tmp <- m

# k2 = 1
m[1, ] <- iprior::dec_plac(tmp[1, ], 2)
m[2, ] <- iprior::dec_plac(tmp[2, ], 1)
m[3:7, ] <- round(tmp[3:7, ])

# k2 = 2
m[8:9, ]   <- iprior::dec_plac(tmp[8:9, ], 3)
m[10:14, ] <- iprior::dec_plac(tmp[10:14, ], 2)

# k2 = 3
m[15:17, ] <- iprior::dec_plac(tmp[15:17, ], 3)
m[18:19, ] <- iprior::dec_plac(tmp[18:19, ], 2)
m[20:21, ] <- iprior::dec_plac(tmp[20:21, ], 1)

# k2 = 4
m[22, ] <- iprior::dec_plac(tmp[22, ], 3)
m[23:25, ] <- iprior::dec_plac(tmp[23:25, ], 2)
m[26:28, ] <- iprior::dec_plac(tmp[26:28, ], 1)

# k2 = 5
m[29, ] <- iprior::dec_plac(tmp[29, ], 3)
m[30:32, ] <- iprior::dec_plac(tmp[30:32, ], 2)
m[33:35, ] <- iprior::dec_plac(tmp[33:35, ], 1)

colnames(m) <- k1
colnames(m)[10] <- "Infinity"
m <- cbind("Area" = rep(as.character(u_format), length(k2)), m)

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE,
      align = c("l", rep("r", length(k1)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$k_1$" = length(k1)), escape = FALSE) %>%
  # collapse_rows(1, latex_hline = "none", row_group_label_position = "stack")
  pack_rows("$k_2=1$", 1, 7, escape = FALSE) %>%
  pack_rows("$k_2=2$", 8, 14, escape = FALSE) %>%
  pack_rows("$k_2=3$", 15, 21, escape = FALSE) %>%
  pack_rows("$k_2=4$", 22, 28, escape = FALSE) %>%
  pack_rows("$k_2=5$", 29, 35, escape = FALSE)
```

\newpage
### Table 4.3: (Continued) Percentiles of the $F$-distribution.

```{r ftab3}
u <- c(0.500, 0.100, 0.050, 0.025, 0.010, 0.005, 0.001)
u_format <- format(u, nsmall = 3)
k1 <- 1:10
k2 <- 6:10
uk2 <- expand.grid(u, k2)
m <- data.frame(matrix(NA, ncol = length(k1), nrow = nrow(uk2)))
for (i in seq_len(nrow(uk2))) {
  for (j in seq_along(k1)) {
    m[i, j] <- qf(1 - uk2[i, 1], df1 = k1[j], df2 = uk2[i, 2])
  }
}
tmp <- m

# k2 = 6
m[1, ] <- iprior::dec_plac(tmp[1, ], 3)
m[2, ] <- iprior::dec_plac(tmp[2, ], 3)
m[3:7, ] <- iprior::dec_plac(tmp[3:7, ], 3)

# k2 = 7
m[8, ]   <- iprior::dec_plac(tmp[8, ], 3)
m[9, ]   <- iprior::dec_plac(tmp[9, ], 3)
m[10:14, ] <- iprior::dec_plac(tmp[10:14, ], 3)

# k2 = 8
m[15, ] <- iprior::dec_plac(tmp[15, ], 3)
m[16:21, ] <- iprior::dec_plac(tmp[16:21, ], 3)

# k2 = 9
m[22, ] <- iprior::dec_plac(tmp[22, ], 3)
m[23:28, ] <- iprior::dec_plac(tmp[23:28, ], 3)

# k2 = 10
m[29, ] <- iprior::dec_plac(tmp[29, ], 3)
m[30:35, ] <- iprior::dec_plac(tmp[30:35, ], 3)

colnames(m) <- k1
m <- cbind("Area" = rep(as.character(u_format), length(k2)), m)

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE,
      align = c("l", rep("r", length(k1)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$k_1$" = length(k1)), escape = FALSE) %>%
  # collapse_rows(1, latex_hline = "none", row_group_label_position = "stack")
  pack_rows("$k_2=6$", 1, 7, escape = FALSE) %>%
  pack_rows("$k_2=7$", 8, 14, escape = FALSE) %>%
  pack_rows("$k_2=8$", 15, 21, escape = FALSE) %>%
  pack_rows("$k_2=9$", 22, 28, escape = FALSE) %>%
  pack_rows("$k_2=10$", 29, 35, escape = FALSE)
```

\newpage
### Table 4.4: (Continued) Percentiles of the $F$-distribution.

```{r ftab4}
u <- c(0.500, 0.100, 0.050, 0.025, 0.010, 0.005, 0.001)
u_format <- format(u, nsmall = 3)
k1 <- c(11, 12, 13, 14, 15, 20, 30, 60, 120, Inf)
k2 <- 6:10
uk2 <- expand.grid(u, k2)
m <- data.frame(matrix(NA, ncol = length(k1), nrow = nrow(uk2)))
for (i in seq_len(nrow(uk2))) {
  for (j in seq_along(k1)) {
    m[i, j] <- qf(1 - uk2[i, 1], df1 = k1[j], df2 = uk2[i, 2])
  }
}
tmp <- m

# k2 = 6
m[1, ] <- iprior::dec_plac(tmp[1, ], 3)
m[2, ] <- iprior::dec_plac(tmp[2, ], 3)
m[3:7, ] <- iprior::dec_plac(tmp[3:7, ], 3)

# k2 = 7
m[8, ]   <- iprior::dec_plac(tmp[8, ], 3)
m[9, ]   <- iprior::dec_plac(tmp[9, ], 3)
m[10:14, ] <- iprior::dec_plac(tmp[10:14, ], 3)

# k2 = 8
m[15, ] <- iprior::dec_plac(tmp[15, ], 3)
m[16:21, ] <- iprior::dec_plac(tmp[16:21, ], 3)

# k2 = 9
m[22, ] <- iprior::dec_plac(tmp[22, ], 3)
m[23:28, ] <- iprior::dec_plac(tmp[23:28, ], 3)

# k2 = 10
m[29, ] <- iprior::dec_plac(tmp[29, ], 3)
m[30:35, ] <- iprior::dec_plac(tmp[30:35, ], 3)

colnames(m) <- k1
colnames(m)[10] <- "Infinity"
m <- cbind("Area" = rep(as.character(u_format), length(k2)), m)

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE,
      align = c("l", rep("r", length(k1)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$k_1$" = length(k1)), escape = FALSE) %>%
  # collapse_rows(1, latex_hline = "none", row_group_label_position = "stack")
  pack_rows("$k_2=6$", 1, 7, escape = FALSE) %>%
  pack_rows("$k_2=7$", 8, 14, escape = FALSE) %>%
  pack_rows("$k_2=8$", 15, 21, escape = FALSE) %>%
  pack_rows("$k_2=9$", 22, 28, escape = FALSE) %>%
  pack_rows("$k_2=10$", 29, 35, escape = FALSE)
```

\newpage
### Table 4.5: (Continued) Percentiles of the $F$-distribution.

```{r ftab5}
u <- c(0.500, 0.100, 0.050, 0.025, 0.010, 0.005, 0.001)
u_format <- format(u, nsmall = 3)
k1 <- 1:10
k2 <- c(11, 12, 13, 14, 15)
uk2 <- expand.grid(u, k2)
m <- data.frame(matrix(NA, ncol = length(k1), nrow = nrow(uk2)))
for (i in seq_len(nrow(uk2))) {
  for (j in seq_along(k1)) {
    m[i, j] <- qf(1 - uk2[i, 1], df1 = k1[j], df2 = uk2[i, 2])
  }
}
tmp <- m

# k2 = 6
m[1, ] <- iprior::dec_plac(tmp[1, ], 3)
m[2, ] <- iprior::dec_plac(tmp[2, ], 3)
m[3:7, ] <- iprior::dec_plac(tmp[3:7, ], 3)

# k2 = 7
m[8, ]   <- iprior::dec_plac(tmp[8, ], 3)
m[9, ]   <- iprior::dec_plac(tmp[9, ], 3)
m[10:14, ] <- iprior::dec_plac(tmp[10:14, ], 3)

# k2 = 8
m[15, ] <- iprior::dec_plac(tmp[15, ], 3)
m[16:21, ] <- iprior::dec_plac(tmp[16:21, ], 3)

# k2 = 9
m[22, ] <- iprior::dec_plac(tmp[22, ], 3)
m[23:28, ] <- iprior::dec_plac(tmp[23:28, ], 3)

# k2 = 10
m[29, ] <- iprior::dec_plac(tmp[29, ], 3)
m[30:35, ] <- iprior::dec_plac(tmp[30:35, ], 3)

colnames(m) <- k1
m <- cbind("Area" = rep(as.character(u_format), length(k2)), m)

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE,
      align = c("l", rep("r", length(k1)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$k_1$" = length(k1)), escape = FALSE) %>%
  # collapse_rows(1, latex_hline = "none", row_group_label_position = "stack")
  pack_rows("$k_2=11$", 1, 7, escape = FALSE) %>%
  pack_rows("$k_2=12$", 8, 14, escape = FALSE) %>%
  pack_rows("$k_2=13$", 15, 21, escape = FALSE) %>%
  pack_rows("$k_2=14$", 22, 28, escape = FALSE) %>%
  pack_rows("$k_2=15$", 29, 35, escape = FALSE)
```

\newpage
### Table 4.6: (Continued) Percentiles of the $F$-distribution.

```{r ftab6}
u <- c(0.500, 0.100, 0.050, 0.025, 0.010, 0.005, 0.001)
u_format <- format(u, nsmall = 3)
k1 <- c(11, 12, 13, 14, 15, 20, 30, 60, 120, Inf)
k2 <- c(11, 12, 13, 14, 15)
uk2 <- expand.grid(u, k2)
m <- data.frame(matrix(NA, ncol = length(k1), nrow = nrow(uk2)))
for (i in seq_len(nrow(uk2))) {
  for (j in seq_along(k1)) {
    m[i, j] <- qf(uk2[i, 1], df1 = k1[j], df2 = uk2[i, 2])
  }
}
tmp <- m

# k2 = 6
m[1, ] <- iprior::dec_plac(tmp[1, ], 3)
m[2, ] <- iprior::dec_plac(tmp[2, ], 3)
m[3:7, ] <- iprior::dec_plac(tmp[3:7, ], 3)

# k2 = 7
m[8, ]   <- iprior::dec_plac(tmp[8, ], 3)
m[9, ]   <- iprior::dec_plac(tmp[9, ], 3)
m[10:14, ] <- iprior::dec_plac(tmp[10:14, ], 3)

# k2 = 8
m[15:16, ] <- iprior::dec_plac(tmp[15:16, ], 3)
m[17:21, ] <- iprior::dec_plac(tmp[17:21, ], 3)

# k2 = 9
m[22:23, ] <- iprior::dec_plac(tmp[22:23, ], 3)
m[24:28, ] <- iprior::dec_plac(tmp[24:28, ], 3)

# k2 = 10
m[29:30, ] <- iprior::dec_plac(tmp[29:30, ], 3)
m[31:35, ] <- iprior::dec_plac(tmp[31:35, ], 3)

colnames(m) <- k1
colnames(m)[10] <- "Infinity"
m <- cbind("Area" = rep(as.character(u), length(k2)), m)

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE,
      align = c("l", rep("r", length(k1)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$k_1$" = length(k1)), escape = FALSE) %>%
  # collapse_rows(1, latex_hline = "none", row_group_label_position = "stack")
  pack_rows("$k_2=11$", 1, 7, escape = FALSE) %>%
  pack_rows("$k_2=12$", 8, 14, escape = FALSE) %>%
  pack_rows("$k_2=13$", 15, 21, escape = FALSE) %>%
  pack_rows("$k_2=14$", 22, 28, escape = FALSE) %>%
  pack_rows("$k_2=15$", 29, 35, escape = FALSE)
```

\newpage
### Table 4.7: (Continued) Percentiles of the $F$-distribution.

```{r ftab7}
u <- c(0.500, 0.100, 0.050, 0.025, 0.010, 0.005, 0.001)
u_format <- format(u, nsmall = 3)
k1 <- 1:10
k2 <- c(20, 30, 60, 120, Inf)
uk2 <- expand.grid(u, k2)
m <- data.frame(matrix(NA, ncol = length(k1), nrow = nrow(uk2)))
for (i in seq_len(nrow(uk2))) {
  for (j in seq_along(k1)) {
    m[i, j] <- qf(uk2[i, 1], df1 = k1[j], df2 = uk2[i, 2])
  }
}
tmp <- m

# k2 = 6
m[1, ] <- iprior::dec_plac(tmp[1, ], 3)
m[2, ] <- iprior::dec_plac(tmp[2, ], 3)
m[3:7, ] <- iprior::dec_plac(tmp[3:7, ], 3)

# k2 = 7
m[8, ]   <- iprior::dec_plac(tmp[8, ], 3)
m[9, ]   <- iprior::dec_plac(tmp[9, ], 3)
m[10:14, ] <- iprior::dec_plac(tmp[10:14, ], 3)

# k2 = 8
m[15, ] <- iprior::dec_plac(tmp[15, ], 3)
m[16:21, ] <- iprior::dec_plac(tmp[16:21, ], 3)

# k2 = 9
m[22, ] <- iprior::dec_plac(tmp[22, ], 3)
m[23:28, ] <- iprior::dec_plac(tmp[23:28, ], 3)

# k2 = 10
m[29, ] <- iprior::dec_plac(tmp[29, ], 3)
m[30:35, ] <- iprior::dec_plac(tmp[30:35, ], 3)

colnames(m) <- k1
m <- cbind("Area" = rep(as.character(u_format), length(k2)), m)

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE,
      align = c("l", rep("r", length(k1)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$k_1$" = length(k1)), escape = FALSE) %>%
  # collapse_rows(1, latex_hline = "none", row_group_label_position = "stack")
  pack_rows("$k_2=20$", 1, 7, escape = FALSE) %>%
  pack_rows("$k_2=30$", 8, 14, escape = FALSE) %>%
  pack_rows("$k_2=60$", 15, 21, escape = FALSE) %>%
  pack_rows("$k_2=120$", 22, 28, escape = FALSE) %>%
  pack_rows("$k_2=\\infty$", 29, 35, escape = FALSE)
```

\newpage
### Table 4.8: (Continued) Percentiles of the $F$-distribution.

```{r ftab8}
u <- c(0.500, 0.100, 0.050, 0.025, 0.010, 0.005, 0.001)
u_format <- format(u, nsmall = 3)
k1 <- c(11, 12, 13, 14, 15, 20, 30, 60, 120, Inf)
k2 <- c(20, 30, 60, 120, Inf)
uk2 <- expand.grid(u, k2)
m <- data.frame(matrix(NA, ncol = length(k1), nrow = nrow(uk2)))
for (i in seq_len(nrow(uk2))) {
  for (j in seq_along(k1)) {
    m[i, j] <- qf(1 - uk2[i, 1], df1 = k1[j], df2 = uk2[i, 2])
  }
}
tmp <- m

# k2 = 6
m[1, ] <- iprior::dec_plac(tmp[1, ], 3)
m[2, ] <- iprior::dec_plac(tmp[2, ], 3)
m[3:7, ] <- iprior::dec_plac(tmp[3:7, ], 3)

# k2 = 7
m[8, ]   <- iprior::dec_plac(tmp[8, ], 3)
m[9, ]   <- iprior::dec_plac(tmp[9, ], 3)
m[10:14, ] <- iprior::dec_plac(tmp[10:14, ], 3)

# k2 = 8
m[15:16, ] <- iprior::dec_plac(tmp[15:16, ], 3)
m[17:21, ] <- iprior::dec_plac(tmp[17:21, ], 3)

# k2 = 9
m[22:23, ] <- iprior::dec_plac(tmp[22:23, ], 3)
m[24:28, ] <- iprior::dec_plac(tmp[24:28, ], 3)

# k2 = 10
m[29:30, ] <- iprior::dec_plac(tmp[29:30, ], 4)
m[31:35, ] <- iprior::dec_plac(tmp[31:35, ], 4)

colnames(m) <- k1
colnames(m)[10] <- "Infinity"
m <- cbind("Area" = rep(as.character(u_format), length(k2)), m)

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE,
      align = c("l", rep("r", length(k1)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$k_1$" = length(k1)), escape = FALSE) %>%
  # collapse_rows(1, latex_hline = "none", row_group_label_position = "stack")
  pack_rows("$k_2=20$", 1, 7, escape = FALSE) %>%
  pack_rows("$k_2=30$", 8, 14, escape = FALSE) %>%
  pack_rows("$k_2=60$", 15, 21, escape = FALSE) %>%
  pack_rows("$k_2=120$", 22, 28, escape = FALSE) %>%
  pack_rows("$k_2=\\infty$", 29, 35, escape = FALSE, bold = FALSE)
```

\newpage
### Table 5: Binomial probabilities (PMF).

The entries in the binomial tables are $X\sim\text{Bin}(n,p)$ where $\Pr(X=k)= \binom{n}{k}p^k\ (1-p)^{n-k} \ \ ; k=0, 1, 2, .., n$.

```{r binomtab1}
prob <- c(0.01, 0.05, seq(0.1, 0.9, by = 0.1), 0.95, 0.99)
n <- 2:8
nlist <- xlist <- list()
for (i in seq_along(n)) {
  xlist[[i]] <- 0:(n[i])
  nlist[[i]] <- rep(n[i], length(xlist[[i]]))
}

tab <- data.frame(
  n = unlist(nlist),
  x = unlist(xlist)
)
for (i in seq_along(prob)) {
  tab <- cbind(tab, dbinom(tab$x, tab$n, prob[i]))
}
colnames(tab) <- c("n", "k", prob)

kable(tab[, -1], booktabs = TRUE, row.names = FALSE, escape = FALSE, digits = 3,
      align = c("l", rep("r", length(prob)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$p$" = length(prob)), escape = FALSE) %>%
  pack_rows("$n=2$", 1, 3, escape = FALSE, bold = FALSE) %>%
  pack_rows("$n=3$", 4, 7, escape = FALSE, bold = FALSE) %>%
  pack_rows("$n=4$", 8, 12, escape = FALSE, bold = FALSE) %>%
  pack_rows("$n=5$", 13, 18, escape = FALSE, bold = FALSE) %>%
  pack_rows("$n=6$", 19, 25, escape = FALSE, bold = FALSE) %>%
  pack_rows("$n=7$", 26, 33, escape = FALSE, bold = FALSE) %>%
  pack_rows("$n=8$", 34, 42, escape = FALSE, bold = FALSE)
```

```{r binomtab2}
prob <- c(0.01, 0.05, seq(0.1, 0.9, by = 0.1), 0.95, 0.99)
n <- 9:12
nlist <- xlist <- list()
for (i in seq_along(n)) {
  xlist[[i]] <- 0:(n[i])
  nlist[[i]] <- rep(n[i], length(xlist[[i]]))
}

tab <- data.frame(
  n = unlist(nlist),
  x = unlist(xlist)
)
for (i in seq_along(prob)) {
  tab <- cbind(tab, dbinom(tab$x, tab$n, prob[i]))
}
colnames(tab) <- c("n", "k", prob)

kable(tab[, -1], booktabs = TRUE, row.names = FALSE, escape = FALSE, digits = 3,
      align = c("l", rep("r", length(prob)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$p$" = length(prob)), escape = FALSE) %>%
  pack_rows("$n=9$", 1, 5, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 6, 10, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows("$n=10$", 11, 15, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 16, 20, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows(" ", 21, 21, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows("$n=11$", 22, 26, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 27, 31, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows(" ", 32, 33, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%  
  pack_rows("$n=12$", 34, 38, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 39, 43, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows(" ", 44, 46, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") 
```


```{r binomtab3}
prob <- c(0.01, 0.05, seq(0.1, 0.9, by = 0.1), 0.95, 0.99)
n <- 13:15
nlist <- xlist <- list()
for (i in seq_along(n)) {
  xlist[[i]] <- 0:(n[i])
  nlist[[i]] <- rep(n[i], length(xlist[[i]]))
}

tab <- data.frame(
  n = unlist(nlist),
  x = unlist(xlist)
)
for (i in seq_along(prob)) {
  tab <- cbind(tab, dbinom(tab$x, tab$n, prob[i]))
}
colnames(tab) <- c("n", "k", prob)

kable(tab[, -1], booktabs = TRUE, row.names = FALSE, escape = FALSE, digits = 3,
      align = c("l", rep("r", length(prob)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$p$" = length(prob)), escape = FALSE) %>%
  pack_rows("$n=13$", 1, 5, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 6, 10, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows(" ", 11, 14, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows("$n=14$", 15, 19, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 20, 24, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows(" ", 25, 29, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows("$n=15$", 30, 34, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 35, 39, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows(" ", 40, 44, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%  
  pack_rows(" ", 45, 45, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") 
```
\newpage
### Table 6: Cummulative Binomial probabilities.
The entries in the binomial tables are $X\sim\text{Bin}(n,p)$ where $\Pr(X \leq k)= \sum_{x=0}^{k}\binom{n}{x}p^x\ (1-p)^{n-x} \ \ $.

```{r, fig.height = 5, fig.width = 8,out.width = "10cm", warning = FALSE, fig.align = "center"}
prob <- c(0.01, 0.05, seq(0.1, 0.9, by = 0.1), 0.95, 0.99)
n <- 2:8
nlist <- xlist <- list()
for (i in seq_along(n)) {
  xlist[[i]] <- 0:(n[i])
  nlist[[i]] <- rep(n[i], length(xlist[[i]]))
}

tab <- data.frame(
  n = unlist(nlist),
  x = unlist(xlist)
)
for (i in seq_along(prob)) {
  tab <- cbind(tab, pbinom(tab$x, tab$n, prob[i]))
}
colnames(tab) <- c("n", "k", prob)

kable(tab[, -1], booktabs = TRUE, row.names = FALSE, escape = FALSE, digits = 3,
      align = c("l", rep("r", length(prob)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$p$" = length(prob)), escape = FALSE) %>%
  pack_rows("$n=2$", 1, 3, escape = FALSE, bold = FALSE) %>%
  pack_rows("$n=3$", 4, 7, escape = FALSE, bold = FALSE) %>%
  pack_rows("$n=4$", 8, 12, escape = FALSE, bold = FALSE) %>%
  pack_rows("$n=5$", 13, 18, escape = FALSE, bold = FALSE) %>%
  pack_rows("$n=6$", 19, 25, escape = FALSE, bold = FALSE) %>%
  pack_rows("$n=7$", 26, 33, escape = FALSE, bold = FALSE) %>%
  pack_rows("$n=8$", 34, 42, escape = FALSE, bold = FALSE)
```
```{r binomtab4}
prob <- c(0.01, 0.05, seq(0.1, 0.9, by = 0.1), 0.95, 0.99)
n <- 9:12
nlist <- xlist <- list()
for (i in seq_along(n)) {
  xlist[[i]] <- 0:(n[i])
  nlist[[i]] <- rep(n[i], length(xlist[[i]]))
}

tab <- data.frame(
  n = unlist(nlist),
  x = unlist(xlist)
)
for (i in seq_along(prob)) {
  tab <- cbind(tab, pbinom(tab$x, tab$n, prob[i]))
}
colnames(tab) <- c("n", "k", prob)

kable(tab[, -1], booktabs = TRUE, row.names = FALSE, escape = FALSE, digits = 3,
      align = c("l", rep("r", length(prob)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$p$" = length(prob)), escape = FALSE) %>%
  pack_rows("$n=9$", 1, 5, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 6, 10, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows("$n=10$", 11, 15, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 16, 20, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows(" ", 21, 21, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows("$n=11$", 22, 26, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 27, 31, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows(" ", 32, 33, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%  
  pack_rows("$n=12$", 34, 38, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 39, 43, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows(" ", 44, 46, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") 
```

```{r binomtab5}
prob <- c(0.01, 0.05, seq(0.1, 0.9, by = 0.1), 0.95, 0.99)
n <- 13:15
nlist <- xlist <- list()
for (i in seq_along(n)) {
  xlist[[i]] <- 0:(n[i])
  nlist[[i]] <- rep(n[i], length(xlist[[i]]))
}

tab <- data.frame(
  n = unlist(nlist),
  x = unlist(xlist)
)
for (i in seq_along(prob)) {
  tab <- cbind(tab, pbinom(tab$x, tab$n, prob[i]))
}
colnames(tab) <- c("n", "k", prob)

kable(tab[, -1], booktabs = TRUE, row.names = FALSE, escape = FALSE, digits = 3,
      align = c("l", rep("r", length(prob)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$p$" = length(prob)), escape = FALSE) %>%
  pack_rows("$n=13$", 1, 5, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 6, 10, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows(" ", 11, 14, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows("$n=14$", 15, 19, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 20, 24, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows(" ", 25, 29, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows("$n=15$", 30, 34, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 35, 39, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows(" ", 40, 44, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%  
  pack_rows(" ", 45, 45, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") 
```

\newpage
### Table 7.1: Poisson Probabilities (PMF).

The entries in the poisson tables are $X\sim\text{Poi}(\lambda)$ where $\Pr(X=k)= \frac{e^{-\lambda}{\lambda}^k}{k!}; k = 0, 1, 2, ..$.

```{r, fig.height = 5, fig.width = 8,out.width = "10cm", warning = FALSE, fig.align = "center"}
# Set the value of lambda
lambda <- 10

# Define the range of x values (number of events)
x <- 0:30

# Create a data frame with x and corresponding probabilities
data <- data.frame(
  x = x,
  probability = dpois(x, lambda)
)

# Create the ggplot
ggplot(data, aes(x = x, y = probability)) +
  geom_bar(stat = "identity", fill = "skyblue", alpha = 0.7) +
  labs(title = "Poisson Distribution (lambda = 10)", 
       x = "Number of Events (k), k = 0, 1, 2, 3, ...", 
       y = "Probability, P(X = k)") +
  theme_minimal()
```

```{r poitab1}
# กำหนดค่า k และ μ
k_values <- 0:10  # ค่า k ที่ต้องการ (0 ถึง 10)
mu_values <- c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1, 1.5, 2, 2.5, 3)

# สร้างตารางเปล่าสำหรับเก็บผลลัพธ์
cumulative_poisson_table <- expand.grid(k = k_values, mu = mu_values) %>%
  mutate(prob = pmap_dbl(list(k, mu), ~ dpois(..1, lambda = ..2))) %>%
  pivot_wider(names_from = mu, values_from = prob) %>%
  arrange(k)

# ปิด warnings และปัดค่าเป็นทศนิยม 3 ตำแหน่ง
suppressWarnings({
  cumulative_poisson_table <- cumulative_poisson_table %>%
    mutate(across(where(is.numeric), \(x) round(x, 3)))
})

# แสดงผลตารางด้วย kable ที่รองรับ LaTeX
cumulative_poisson_table %>%
  kbl(format = "latex", booktabs = TRUE, align = "c") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE) %>%
  add_header_above(c(" " = 1, "lambda" = length(mu_values))) %>%
  kable_styling(latex_options = "scale_down", position = "center")
```


\newpage
### Table 7.2: (Continued) Poisson Probabilities.

```{r poitab2}
# กำหนดค่า k และ μ
k_values <- 0:23  # ค่า k ที่ต้องการ (0 ถึง 10)
mu_values <- c(3.5, 4, 4.5, 5, 5.5, 6, 6.5, 7, 7.5, 8, 8.5, 9, 9.5, 10)

# สร้างตารางเปล่าสำหรับเก็บผลลัพธ์
cumulative_poisson_table <- expand.grid(k = k_values, mu = mu_values) %>%
  mutate(prob = pmap_dbl(list(k, mu), ~ dpois(..1, lambda = ..2))) %>%
  pivot_wider(names_from = mu, values_from = prob) %>%
  arrange(k)

# ปิด warnings และปัดค่าเป็นทศนิยม 3 ตำแหน่ง
suppressWarnings({
  cumulative_poisson_table <- cumulative_poisson_table %>%
    mutate(across(where(is.numeric), \(x) round(x, 3)))
})

# แสดงผลตารางด้วย kable ที่รองรับ LaTeX
cumulative_poisson_table %>%
  kbl(format = "latex", booktabs = TRUE, align = "c") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE) %>%
  add_header_above(c(" " = 1, "lambda" = length(mu_values))) %>%
  kable_styling(latex_options = "scale_down", position = "center")
```

\newpage
### Table 7.3: (Continued) Poisson Probabilities.

```{r poitab3}
# กำหนดค่า k และ μ
k_values <- 0:40  # ค่า k ที่ต้องการ (0 ถึง 10)
mu_values <- c(11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 25, 30, 40, 50)

# สร้างตารางเปล่าสำหรับเก็บผลลัพธ์
cumulative_poisson_table <- expand.grid(k = k_values, mu = mu_values) %>%
  mutate(prob = pmap_dbl(list(k, mu), ~ dpois(..1, lambda = ..2))) %>%
  pivot_wider(names_from = mu, values_from = prob) %>%
  arrange(k)

# ปิด warnings และปัดค่าเป็นทศนิยม 3 ตำแหน่ง
suppressWarnings({
  cumulative_poisson_table <- cumulative_poisson_table %>%
    mutate(across(where(is.numeric), \(x) round(x, 3)))
})

# แสดงผลตารางด้วย kable ที่รองรับ LaTeX
cumulative_poisson_table %>%
  kbl(format = "latex", booktabs = TRUE, align = "c") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE) %>%
  add_header_above(c(" " = 1, "lambda" = length(mu_values))) %>%
  kable_styling(latex_options = "scale_down", position = "center")
```
\newpage
### Table 8.1: Cummulative Poisson Probabilities

The entries in the poisson tables are $X\sim\text{Poi}(\lambda)$ where $\Pr(X \leq k)= \sum_{x=0}^{k} \frac{e^{-\lambda}{\lambda}^x}{x!}$.

```{r, fig.height = 5, fig.width = 8,out.width = "10cm", warning = FALSE, fig.align = "center"}
# Set the value of lambda
lambda <- 10

# Define the range of x values (number of events)
x <- 0:20

# Create a data frame with x and corresponding probabilities
data <- data.frame(
  x = x,
  probability = ppois(x, lambda)
)

# Create the ggplot
ggplot(data, aes(x = x, y = probability)) +
  geom_bar(stat = "identity", fill = "skyblue", alpha = 0.7) +
  labs(title = "Poisson Distribution (lambda = 10)", 
       x = "Number of Events (k), k = 0, 1, 2, 3, ...", 
       y = "Cummulative Probability, P(X <= k)") +
  theme_minimal()
```

```{r poitab4}
# กำหนดค่า k และ μ
k_values <- 0:10  # ค่า k ที่ต้องการ (0 ถึง 10)
mu_values <- c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1, 1.5, 2, 2.5, 3)

# สร้างตารางเปล่าสำหรับเก็บผลลัพธ์
cumulative_poisson_table <- expand.grid(k = k_values, mu = mu_values) %>%
  mutate(prob = pmap_dbl(list(k, mu), ~ ppois(..1, lambda = ..2))) %>%
  pivot_wider(names_from = mu, values_from = prob) %>%
  arrange(k)

# ปิด warnings และปัดค่าเป็นทศนิยม 3 ตำแหน่ง
suppressWarnings({
  cumulative_poisson_table <- cumulative_poisson_table %>%
    mutate(across(where(is.numeric), \(x) round(x, 3)))
})

# แสดงผลตารางด้วย kable ที่รองรับ LaTeX
cumulative_poisson_table %>%
  kbl(format = "latex", booktabs = TRUE, align = "c") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE) %>%
  add_header_above(c(" " = 1, "lambda" = length(mu_values))) %>%
  kable_styling(latex_options = "scale_down", position = "center")
```

\newpage
### Table 8.2: (Continued) Cummulative Poisson Probabilities.

```{r poitab5}
# กำหนดค่า k และ μ
k_values <- 0:23  # ค่า k ที่ต้องการ (0 ถึง 10)
mu_values <- c(3.5, 4, 4.5, 5, 5.5, 6, 6.5, 7, 7.5, 8, 8.5, 9, 9.5, 10)

# สร้างตารางเปล่าสำหรับเก็บผลลัพธ์
cumulative_poisson_table <- expand.grid(k = k_values, mu = mu_values) %>%
  mutate(prob = pmap_dbl(list(k, mu), ~ ppois(..1, lambda = ..2))) %>%
  pivot_wider(names_from = mu, values_from = prob) %>%
  arrange(k)

# ปิด warnings และปัดค่าเป็นทศนิยม 3 ตำแหน่ง
suppressWarnings({
  cumulative_poisson_table <- cumulative_poisson_table %>%
    mutate(across(where(is.numeric), \(x) round(x, 3)))
})

# แสดงผลตารางด้วย kable ที่รองรับ LaTeX
cumulative_poisson_table %>%
  kbl(format = "latex", booktabs = TRUE, align = "c") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE) %>%
  add_header_above(c(" " = 1, "lambda" = length(mu_values))) %>%
  kable_styling(latex_options = "scale_down", position = "center")
```
\newpage
### Table 8.3: (Continued) Cummulative Poisson Probabilities.

```{r poitab6}
# กำหนดค่า k และ μ
k_values <- 0:40  # ค่า k ที่ต้องการ (0 ถึง 10)
mu_values <- c(11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 25, 30, 40, 50)

# สร้างตารางเปล่าสำหรับเก็บผลลัพธ์
cumulative_poisson_table <- expand.grid(k = k_values, mu = mu_values) %>%
  mutate(prob = pmap_dbl(list(k, mu), ~ ppois(..1, lambda = ..2))) %>%
  pivot_wider(names_from = mu, values_from = prob) %>%
  arrange(k)

# ปิด warnings และปัดค่าเป็นทศนิยม 3 ตำแหน่ง
suppressWarnings({
  cumulative_poisson_table <- cumulative_poisson_table %>%
    mutate(across(where(is.numeric), \(x) round(x, 3)))
})

# แสดงผลตารางด้วย kable ที่รองรับ LaTeX
cumulative_poisson_table %>%
  kbl(format = "latex", booktabs = TRUE, align = "c") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE) %>%
  add_header_above(c(" " = 1, "lambda" = length(mu_values))) %>%
  kable_styling(latex_options = "scale_down", position = "center")
```




